### 2011-01-03 docs/slides/model.tex
Predator section complete.

\frame
{
	\frametitle{The Predator}
	\framesubtitle{Design of Memory}
}

\frame
{
	\frametitle{The Predator}
	\framesubtitle{Attack Algorithm}
}

\frame
{
	\frametitle{The Predator}
	\framesubtitle{Genome}
}

\frame
{
	\frametitle{The Predator}
	\framesubtitle{Mobility}
}

\frame
{
	\frametitle{The Predator}
	\framesubtitle{Reproduction process}
}

>>>>

\frame
{
	\frametitle{The Predator}
	\framesubtitle{Design of Memory}

	\begin{itemize}
		\item Input to Memory:
			\begin{itemize}
				\item Each prey has an evolving CA represented by a binary Genome.
				\item This 2D pattern is serialized to a 1D binary array.
				\item Binary representation is converted to bipolar representation.
			\end{itemize}
		\item Pattern Recognition with Hopfield Network:
			\begin{itemize}
				\item Learning: Apply Hebbian learning to calculate weights.
				\item Initialization: Input to the network is initialized with value of the input vector.
				\item Iterate Until Convergence: Each neuron is updated asynchronously with the input of its previous state until convergence.
				\item Output: Finally a pattern is set as output when the network reaches convergence.
			\end{itemize}
	\end{itemize}
}

\frame
{
	\frametitle{The Predator}
	\framesubtitle{Attack Algorithm}

	\begin{itemize}
		\item When agent reaches `Minimum Attack Age' it starts hunting.
		\item Select a random prey within vicinity (same cell).
		\item Attack process involves recognition of prey pattern.
		\item Two parameters to limit pattern memorization and recognition process as both are computationally expensive.
			\begin{itemize}
				\item Hopfield Minimum Memory Size (value 2 to 6)
				\item Hopfield Maximum Memory Size (value 10)
			\end{itemize}
		\item New predator attacks without caution. 
		\item Attacks everyone and in the process store pattern and palatability.
		\item When memory reaches `Hopfield Minimum Memory Size': intelligent selection.
	\end{itemize}
}

\frame
{
	\frametitle{The Predator}
	\framesubtitle{Genome}

	\begin{table}
	\centering
	\begin{scriptsize}
	\begin{spacing}{1.5}
	\begin{tabular}{|c|c|}
		\hline
			\textbf{Mobility(4)} & \textbf{Reproduction(1)} \\ \hline
					 1101					   &					1						 		\\ \hline
	\end{tabular}
	\end{spacing}
	\end{scriptsize}
	\caption{Distribution and purpose of each gene of the 5 bit predator genome.}
	\label{tab:predator-genome}
	\end{table}
}

\frame
{
	\frametitle{The Predator}
	\framesubtitle{Mobility}

	\begin{itemize}
		\item First 4 bits of the genome calculated to evaluate the magnitude of force of movement.
		\item Direction is decided based on the number of prey species present in a neighboring cell.
		\item Move towards the cell with least number of predator and most number of prey.
		\item This is such that predators are distributed all over the environment.
		\item Increases agent's predatory behavior.
	\end{itemize}
}

\frame
{
	\frametitle{The Predator}
	\framesubtitle{Reproduction process}

	\begin{itemize}
		\item Agent reaches reproduction age.
		\item Agent exceeds reproduction age interval, which is difference in time between two reproduction activity.
		\item Agent is capable of reproduction depending on 5th gene.
		\item Select another predator from same cell which satisfy above conditions.
		\item Perform crossover and mutation to create another predator.
		\item Predator is initialized with zero memory.
	\end{itemize}
}
